combined

### 2021-08-19 analysis/bayes_droplet.Rmd
as

```{r}
library(tidyverse)
library(emmeans)
library(brms)
library(bayestestR)
library(modelbased)
library(ggtext)
library(patchwork)
library(ggthemes)
```

@@

```{r}
options(scipen = 999)
estimate_contrasts(model13, test = "bf") %>% 
  as_tibble() -> bf_dv10
write_csv(x = bf_dv10, file = "bf_dv10.csv")
```

@@

```{r}
estimate_contrasts(model23, test = "bf")
```

@@

@@

```{r}
estimate_contrasts(model43, test = "bf")
```

@@

```{r}
emmeans5$emmeans %>% 
  as_tibble() %>% 
  unite("trt", c("solution", "nozzle"), sep = " - ") %>% 
  ggplot(aes(x = fct_reorder(trt, response), y = response*100)) +
  geom_point() +
  geom_linerange(aes(ymin = lower.HPD*100, ymax = upper.HPD*100)) +
  coord_flip() +
  theme_classic() +
  labs(title = "<200 droptlet")
```

```{r}
estimate_contrasts(model53, test = "bf")
```

```{r}
emmeans1$emmeans %>% as_tibble() %>% mutate(type = "DV10") -> em1
emmeans2$emmeans %>% as_tibble() %>% mutate(type = "DV50") -> em2
emmeans3$emmeans %>% as_tibble() %>% mutate(type = "DV90") -> em3
```
-> emm
```{r}
em1 %>% 
  bind_rows(em2) %>% 
  bind_rows(em3) %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  mutate(type = fct_recode(type,
                          "D<sub>v10</sub>" = "DV10",
                          "D<sub>v50</sub>" = "DV50",
                          "D<sub>v90</sub>" = "DV90")) -> emm
```

```{r}
droplet %>% 
  pivot_longer(3:5, names_to = "type", values_to = "response") %>%
  mutate(type = str_to_upper(type)) %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  dplyr::select(-rs, -x200, -rep) %>% 
  mutate(type = fct_recode(type,
                          "D<sub>v10</sub>" = "DV10",
                          "D<sub>v50</sub>" = "DV50",
                          "D<sub>v90</sub>" = "DV90")) -> droplet1
```

```{r}
library(ggthemes)
emm %>% 
  ggplot(aes(x = fct_reorder(trt, response), y = response, color = trt)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.3) +
  geom_jitter(data = droplet1, alpha = 0.1, size = 2) +
  facet_grid(~ type) +
  coord_flip() +
  labs(x = NULL, y = "Droplet size (µm)") +
  scale_color_viridis_d(option = "C") +
  theme_few() + 
  theme(strip.text = element_markdown(size = 12),
        legend.position = "none") -> dv
```

```{r}
emmeans4$emmeans %>% as_tibble() -> em4
emmeans5$emmeans %>% as_tibble() -> em5
```

```{r}
droplet %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  dplyr::select(trt, rs) %>% 
  rename(response = rs) -> droplet2
```

```{r}
em4 %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  ggplot(aes(x = fct_reorder(trt, response), y = response, color = trt)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.3) +
  geom_jitter(data = droplet2, alpha = 0.1, size = 2) +
  coord_flip() +
  labs(x = NULL, y = "RS") +
  scale_color_viridis_d(option = "C") +
  theme_few() + 
  theme(strip.text = element_markdown(),
        legend.position = "none") -> rs
```

```{r}
droplet %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  dplyr::select(trt, x200) %>% 
  rename(response = x200) -> droplet3
```

```{r}
(
em5 %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  ggplot(aes(x = fct_reorder(trt, response*100), y = response*100, color = trt)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD*100, ymax = upper.HPD*100), size = 1.3) +
  geom_jitter(data = droplet3, alpha = 0.1, size = 2) +
  coord_flip() +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8)) +
  labs(x = NULL, y = "% drifable fines < 200 µm") +
  scale_color_viridis_d(option = "C") +
  theme_few() + 
  theme(strip.text = element_markdown(),
        legend.position = "none") -> x200
)
```

```{r}
rs + x200 -> fig
dv / fig -> fig1

ggsave("Figure 4.png", width = 9, height = 6)
```

>>>>

```{r}
library(tidyverse)
library(emmeans)
library(brms)
library(bayestestR)
library(modelbased)
library(ggtext)
library(patchwork)
library(ggrepel)
library(ggthemes)
```

@@

```{r}
#https://easystats.github.io/blog/posts/bayestestr_emmeans/
dv10_main <- pairs(emmeans(model13, ~ solution * nozzle))

describe_posterior(dv10_main,
                   centrality = "mean", dispersion = TRUE,
                   ci = .95, ci_method = "hdi",
                   test = c("bayesfactor"),
                   bf_prior = model13) %>% 
  tibble() -> dv10_bf
readr::write_csv(path = "../supp_file/data/bf_dv10.csv", x = dv10_bf)
```

```{r}
#options(scipen = 999)
#estimate_contrasts(model13, test = "bf") %>% 
#  as_tibble() -> bf_dv10
#write_csv(x = bf_dv10, file = "bf_dv10.csv")
```

@@

```{r}
#https://easystats.github.io/blog/posts/bayestestr_emmeans/
dv50_main <- pairs(emmeans(model23, ~ nozzle * solution))

describe_posterior(dv50_main,
                   centrality = "mean", dispersion = TRUE,
                   ci = .95, ci_method = "hdi",
                   test = c("bayesfactor"),
                   bf_prior = model23) %>% 
  tibble() -> dv50_bf
readr::write_csv(path = "../supp_file/data/bf_dv50.csv", x = dv50_bf)
```

```{r}
estimate_contrasts(model23, test = "bf", transform = "response")
```

@@

```{r}
#https://easystats.github.io/blog/posts/bayestestr_emmeans/
dv90_main <- pairs(emmeans(model33, ~ nozzle * solution))

describe_posterior(dv90_main,
                   centrality = "mean", dispersion = TRUE,
                   ci = .95, ci_method = "hdi",
                   test = c("bayesfactor"),
                   bf_prior = model33) %>% 
  tibble() -> dv90_bf
readr::write_csv(path = "../supp_file/data/bf_dv90.csv", x = dv90_bf)
```

@@

```{r}
rs_main <- pairs(emmeans(model43, ~ nozzle * solution))

describe_posterior(rs_main,
                   centrality = "mean", dispersion = TRUE,
                   ci = .95, ci_method = "hdi",
                   test = c("bayesfactor"),
                   bf_prior = model43) %>% 
  tibble() -> rs_bf
readr::write_csv(path = "../supp_file/data/bf_rs.csv", x = rs_bf)
```

@@

```{r}
duz_main <- pairs(emmeans(model53, ~ nozzle * solution))

describe_posterior(duz_main,
                   centrality = "mean", dispersion = TRUE,
                   ci = .95, ci_method = "hdi",
                   test = c("bayesfactor"),
                   bf_prior = model53) %>% 
  tibble() -> duz_bf
readr::write_csv(path = "../supp_file/data/bf_duz.csv", x = duz_bf)
```

```{r}
emmeans1$emmeans %>% as_tibble() %>% mutate(type = "DV10") -> em1
emmeans2$emmeans %>% as_tibble() %>% mutate(type = "DV50") -> em2
emmeans3$emmeans %>% as_tibble() %>% mutate(type = "DV90") -> em3
```

```{r}
em1 %>% 
  bind_rows(em2) %>% 
  bind_rows(em3) %>% 
  mutate(solution = str_replace(solution, "water", "")) %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  mutate(trt = str_remove(trt, "^[^a-zA-Z]+")) %>%
  mutate(trt = str_remove(trt, "Water-")) %>% 
  mutate(type = fct_recode(type,
                          "D<sub>v10</sub>" = "DV10",
                          "D<sub>v50</sub>" = "DV50",
                          "D<sub>v90</sub>" = "DV90")) -> emm
```

```{r}
droplet %>% 
  pivot_longer(3:5, names_to = "type", values_to = "response") %>%
  mutate(type = str_to_upper(type)) %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  mutate(trt = str_remove(trt, "^[^a-zA-Z]+")) %>%
  dplyr::select(-rs, -x200, -rep) %>% 
  mutate(trt = str_remove(trt, "Water-")) %>% 
  mutate(type = fct_recode(type,
                          "D<sub>v10</sub>" = "DV10",
                          "D<sub>v50</sub>" = "DV50",
                          "D<sub>v90</sub>" = "DV90")) -> droplet1
```

```{r}
emm %>% 
  mutate(response = round(response, 1)) %>% 
  ggplot(aes(x = fct_reorder(trt, response), 
             y = response, 
             color = trt, 
             shape = type)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD),
                 position = position_dodge2(width = 0.4), 
                 size = 1.3, alpha = 0.5) +
  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
  geom_jitter(data = droplet1,
                position = position_dodge2(width = 0.4),
              mapping = aes(color = trt, shape = type), alpha = 0.1, size = 2) +
  coord_flip() +
  geom_text_repel(aes(label = response, 
                         x = trt, color = trt, shape = type),
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 455) +
  labs(x = NULL, y = "Droplet size (µm)", color = NULL, shape = NULL) +
  scale_color_viridis_d(option = "H") +
  scale_y_continuous(limits = c(0, 1500), breaks = seq(0, 1500, 300)) +
  scale_shape_manual(values = c(8,9,10)) +
  theme_few() + 
  theme(legend.position = c(0.85, 0.2),
        legend.text = element_markdown(size = 20),
        legend.background = element_blank(),
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) +
  guides(color = "none") -> fig1

ggsave("fig.png")
```

```{r warning = FALSE}
fig1 + fig2 + fig3 +
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 35, hjust = 0, vjust = 0))

ggsave("Figure 5.png", width = 11, height = 4)
```

```{r}
emmeans4$emmeans %>% as_tibble() %>% 
  mutate(solution = str_replace(solution, "Water", "")) %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
    mutate(trt = str_remove(trt, "^[^a-zA-Z]+")) -> em4
emmeans5$emmeans %>% as_tibble() -> em5
```

```{r}
droplet %>% 
  mutate(solution = str_replace(solution, "Water", "")) %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  dplyr::select(trt, rs) %>% 
  mutate(trt = str_remove(trt, "^[^a-zA-Z]+")) %>%
  rename(response = rs) -> droplet2
```

```{r}
em4 %>% 
  mutate(response = round(response, 2)) %>% 
  ggplot(aes(x = fct_reorder(trt, response), y = response, color = trt)) +
  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD),
                 position = position_dodge2(width = 0.4), size = 1.3) +
  coord_flip() +
  geom_jitter(data = droplet2,
              mapping = aes(color = trt), alpha = 0.1, size = 2) +
  geom_text_repel(aes(label = response, 
                         x = trt),
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 455) +
#  annotate("text", x = 5, y = 0.1, label = "There are differences \namong all pairwise trt  \ncomparisons (P <.0001) \nin figures A, B and C", size = 9, hjust = 0, lineheight = 0.3,
#           color = 1, fontface = "italic") +
  labs(x = NULL, y = "Relative span", color = NULL) +
  scale_color_viridis_d(option = "H") +
  scale_y_continuous(limits = c(0, 1.2), breaks = seq(0, 1.2, 0.2)) +
  theme_few() + 
  theme(legend.position = "none",
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) -> fig2
```

```{r}
emmeans5$emmeans %>% as_tibble() %>% 
  mutate(solution = str_replace(solution, "Water", "")) %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  mutate(trt = str_remove(trt, "^[^a-zA-Z]+")) -> em5
```

```{r}
droplet %>% 
  mutate(solution = str_replace(solution, "Water", "")) %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  dplyr::select(trt, x200) %>% 
  rename(response = x200) %>% 
  mutate(trt = str_remove(trt, "^[^a-zA-Z]+")) -> droplet3
```

```{r}
em5 %>% 
  mutate(response = round(response, 4)) %>% 
  ggplot(aes(x = fct_reorder(trt, response*100), y = response*100, color = trt)) +
  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
  geom_linerange(aes(ymin = lower.HPD*100, ymax = upper.HPD*100),
                 position = position_dodge2(width = 0.4), size = 1.3) +
  coord_flip() +
  geom_jitter(data = droplet2, 
              mapping = aes(color = trt), alpha = 0.1, size = 2) +
  geom_text_repel(aes(label = response*100, 
                         x = trt),
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 455) +
#  annotate("text", x = 2, y = 3, label = "There are differences \namong all pairwise trt \ncomparisons (P <.0001)", size = 9, hjust = 0, lineheight = 0.3,
#           color = 1, fontface = "italic") +
  labs(x = NULL, y = "% driftable fines < 200 µm", color = NULL) +
  scale_color_viridis_d(option = "H") +
  scale_y_continuous(limits = c(0, 10), breaks = seq(0, 10, 2)) +
  theme_few() + 
  theme(legend.position = "none",
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) -> fig3
```

```{r warning = FALSE}
fig1 + fig2 + fig3 +
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 35, hjust = 0, vjust = 0))

ggsave("Figure 5.png", width = 11, height = 4)
```

### 2021-08-19 analysis/combined.Rmd
as

```{r}
new_dt %>% 
  unite("trt", c("solution", "sprayer", "nozzle"), 
        sep = "-", remove = FALSE) -> new_dt 
```

@@

```{r}
### Filter deposition dataset inswath
inswath <-  new_dt %>% 
  filter(type == "inswath") %>% 
  filter(!is.na(deposition)) %>% 
  mutate(trt = str_replace(trt, "Intact", "DRA")) 
```

@@

@@

library(modelbased)
estimate_contrasts(model1, test = "bf")
```

```{r}
estimate_contrasts(model1, test = "bf") -> inswath_bf
inswath_bf %>% 
  tibble() -> inswath_bf
#readr::write_csv(path = "inswath_bf.csv", x = inswath_bf)
```

```{r}
library(ggrepel)
em %>% as_tibble() %>% 
  mutate(sprayer = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  mutate(emmean = round(emmean, 1)) %>% 
  ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
             color = trt, shape = sprayer, label = emmean)) +
  geom_point(size = 3) +
  geom_jitter(data = inswath %>% 
                rename(emmean = deposition), alpha = 0.1) +
  scale_color_viridis_d(option = "H") +
  coord_flip() +
  geom_text_repel(  size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 455) +
  scale_shape_manual(values = c(16, 1)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.2) +
  ylim(0, 2000) +
  theme_few(base_family = "lato") +
  labs(x = NULL, y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")"))) +
  theme(legend.position = "none",
        axis.title = element_text(size = 30),
        axis.text = element_text(size = 25)) -> figA

@@

library(modelbased)
estimate_contrasts(model2, test = "bf") -> upwind_bf
upwind_bf %>% 
  tibble() -> upwind_bf
#readr::write_csv(path = "upwind_bf.csv", x = upwind_bf)
```

@@

```{r include=TRUE}
c <- distance_final1 %>% 
  mutate(trt = str_replace(trt, "Intact", "DRA")) %>% 
  mutate(hood = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  mutate(distance_m = round(distance_m, 1)) %>% 
  ggplot(aes(x = fct_reorder(trt, distance_m), 
             y = distance_m,
             label = distance_m, color = trt, shape = hood)) +
  geom_point(size = 3, stroke = 1) +
  geom_text_repel(
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 545) +
  scale_shape_manual(values = c(16, 1)) +
  geom_segment(aes(x= trt, xend= trt, y=0, yend=distance_m), size = 2) +
  coord_flip() +
  scale_color_viridis_d(option = "H") + 
  labs(y = "Predicted distance (m)", x = NULL) +
  ylim(0,60) +
  theme_few(base_family = "lato") +
  theme(legend.position = "none",
        legend.text = element_markdown(size = 20),
        legend.background = element_blank(),
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) 
c
```

@@

```{r include=TRUE}
figs <- fig2 %>% 
  mutate(trt = str_replace(trt, "Intact", "DRA")) %>% 
  mutate(hood = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  ggplot(aes(x = distance_m, y = predicted, color = trt, 
             fill = trt, label = formula, shape = hood)) +
  scale_color_viridis_d(option = "H") + 
  scale_fill_viridis_d(option = "H") + 
  geom_line(fill = NA) +
  geom_point(alpha = 0.5) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), 
              alpha = 0.3, color = NA) +
  facet_wrap(~ trt, ncol = 3) +
  scale_shape_manual(values = c(16, 1)) + 
  theme_few(base_family = "lato") +
  geom_label(aes(label = formula), x = 30, y = 20, color = "white", size = 10) +
  labs(x = "Distance (m)", 
       y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")"))) +
  theme(legend.position = "none",
        legend.text = element_markdown(size = 20),
        legend.background = element_blank(),
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25),
        strip.background = element_blank(),
        strip.text = element_textbox(
          size = 30,
          color = "white", 
          fill = "#494949", 
          box.color = "#282728",
          halign = 0.5, linetype = 1, r = unit(5, "pt"), width = unit(1, "npc"),
          padding = margin(2, 0, 1, 0), 
          margin = margin(3, 3, 3, 3)))

@@

```{r}
auc_data1 <- auc_data %>% 
  filter(distance_m == 1) %>% 
  mutate(trt = str_replace(trt, "Intact", "DRA")) 
```

@@

```{r}
epred3$emmeans %>% as_tibble() %>% 
  mutate(sprayer = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  mutate(emmean = round(emmean, 1)) %>% 
  ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
             color = trt, shape = sprayer, label = emmean)) +
  geom_point(size = 3) +
  geom_jitter(data = auc_data %>% 
                rename(emmean = auc), alpha = 0.02) +
  scale_color_viridis_d(option = "H") +
  geom_text_repel(
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 545) +
  coord_flip() +
  scale_shape_manual(values = c(16, 1)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.2) +
  scale_y_continuous(breaks = c(0, 50, 100, 150, 200, 250)) +
  theme_few(base_family = "lato") +
  labs(x = NULL, y = "Area under the curve") +
  theme(legend.position = "none",
        legend.text = element_markdown(size = 20),
        legend.background = element_blank(),
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) -> figE
figE
```

```{r}
estimate_contrasts(auc_model, test = "bf") -> auc_bf
auc_bf %>% 
  tibble() -> auc_bf
readr::write_csv(path = "auc_bf.csv", x = auc_bf)
```

```{r eval = FALSE}
library(modelbased)
estimate_contrasts(auc_model, test = "bf") %>% 
  kableExtra::kable()
```

>>>>

```{r}
new_dt %>% 
  mutate(solution= str_replace(solution, "Water", "")) %>% 
  unite("trt", c("solution", "sprayer", "nozzle"), 
        sep = "-", remove = FALSE) %>% 
  mutate(trt = str_replace(trt, "Intact", "DRA")) %>% 
  mutate(trt = str_remove(trt, "^[^a-zA-Z]+")) -> new_dt  
```

@@

```{r}
### Filter deposition dataset inswath
inswath <-  new_dt %>% 
  filter(type == "inswath") %>% 
  filter(!is.na(deposition))
```

@@

```{r}
#https://easystats.github.io/bayestestR/articles/bayes_factors.html
#https://www.statisticshowto.com/bayes-factor-definition/
groups <- emmeans(model1, ~ trt)
group_diff <- pairs(groups)
(groups_all <- rbind(groups, group_diff))

@@

library(modelbased)
estimate_contrasts(model1, test = "bf")
```
```{r}
#https://easystats.github.io/blog/posts/bayestestr_emmeans/
inswath_main <- pairs(emmeans(model1, ~ trt))

describe_posterior(inswath_main,
                   centrality = "mean", dispersion = TRUE,
                   ci = .95, ci_method = "hdi",
                   test = c("bayesfactor"),
                   bf_prior = model1) %>% 
  tibble() -> inswath_bf
readr::write_csv(path = "../supp_file/data/inswath_bf.csv", x = inswath_bf)
```

```{r}
#estimate_contrasts(model1, test = "bf") -> inswath_bf
#inswath_bf %>% 
#  tibble() -> inswath_bf
#readr::write_csv(path = "../supp_file/data/inswath_bf.csv", x = inswath_bf)
```

```{r}
library(ggrepel)
em %>% as_tibble() %>% 
  mutate(sprayer = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  mutate(emmean = round(emmean, 1)) %>% 
  ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
             color = trt, shape = sprayer, label = emmean)) +
  geom_point(size = 3) +
  geom_jitter(data = inswath %>% 
                rename(emmean = deposition), alpha = 0.1) +
  scale_color_viridis_d(option = "H") +
  coord_flip() +
  geom_text_repel(  size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 455) +
  scale_shape_manual(values = c(16, 1)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.2) +
  ylim(0, 2000) +
  theme_few() +
  labs(x = NULL, 
       y = expression(paste("Spray particle deposition (\u03B7L/cm"^"2",")"))
       ) +
  theme(legend.position = "none",
        axis.title = element_text(size = 30),
        axis.text = element_markdown(size = 25)) -> figA

@@

library(modelbased)
estimate_contrasts(model2, test = "bf") -> upwind_bf
upwind_bf %>% 
  tibble() -> upwind_bf
readr::write_csv(path = "../supp_file/data/upwind_bf.csv", x = upwind_bf)
```

@@

```{r include=TRUE}
c <- distance_final1 %>% 
  mutate(trt = str_replace(trt, "Intact", "DRA")) %>% 
  mutate(hood = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  mutate(distance_m = round(distance_m, 1)) %>% 
  ggplot(aes(x = fct_reorder(trt, distance_m), 
             y = distance_m,
             label = distance_m, color = trt, shape = hood)) +
  geom_point(size = 3, stroke = 1) +
  geom_text_repel(
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 545) +
  scale_shape_manual(values = c(16, 1)) +
  geom_segment(aes(x= trt, xend= trt, y=0, yend=distance_m), size = 1) +
  coord_flip() +
  scale_color_viridis_d(option = "H") + 
  labs(y = "Predicted distance (m)", x = NULL) +
  ylim(0,60) +
  theme_few(base_family = "lato") +
  theme(legend.position = "none",
        legend.text = element_markdown(size = 20),
        legend.background = element_blank(),
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) 
c
```

@@

```{r}
loc <- tibble(trt = "DRA-Open-TTI")
```

```{r include=TRUE}
fig2 %>% 
  mutate(trt = str_replace(trt, "Intact", "DRA")) %>% 
  mutate(hood = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  ggplot(aes(x = distance_m, y = predicted, color = trt, 
             fill = trt, label = formula, shape = hood)) +
  scale_color_viridis_d(option = "H") + 
  scale_fill_viridis_d(option = "H") + 
  geom_line(fill = NA) +
  geom_point(alpha = 0.5) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), 
              alpha = 0.3, color = NA) +
  facet_wrap(~ trt, ncol = 3) +
  scale_shape_manual(values = c(16, 1)) + 
  theme_few() +
  geom_text(data = loc, mapping = aes(x = 10, y = 20), 
            label = "Intercept", inherit.aes = FALSE, size = 10) +
  geom_text(data = loc, mapping = aes(x = 55, y = 10), 
            label = "Slope", inherit.aes = FALSE, size = 10) +
  geom_label(aes(label = formula), x = 30, y = 15, color = "white", size = 12) +
  geom_curve(data = loc, mapping = aes(x = 25, y = 17,
             xend = 20, yend = 20),
             arrow = arrow(length = unit(0.07, "inch")), 
             color = 1,
             size = 0.4, curvature = 0.3, inherit.aes = FALSE) +
  geom_curve(data = loc, mapping = aes(x = 42, y = 13,
             xend = 47, yend = 10),
             arrow = arrow(length = unit(0.07, "inch")), 
             color = 1,
             size = 0.4, curvature = 0.3, inherit.aes = FALSE) +
  labs(x = "Distance (m)", 
       y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")"))) +
  theme(legend.position = "none",
        legend.text = element_markdown(size = 20),
        legend.background = element_blank(),
        axis.title = element_markdown(size = 32),
        axis.text = element_markdown(size = 28),
        strip.background = element_blank(),
        strip.text = element_textbox(
          size = 32,
          face = "bold",
          color = "white", 
          fill = "#494949", 
          box.color = "#282728",
          halign = 0.5, linetype = 1, r = unit(5, "pt"), width = unit(1, "npc"),
          padding = margin(2, 0, 1, 0), 
          margin = margin(3, 3, 3, 3)))

@@

```{r}
auc_data1 <- auc_data %>% 
  filter(distance_m == 1)
```

@@

```{r}
epred3$emmeans %>% as_tibble() %>% 
  mutate(sprayer = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  mutate(emmean = round(emmean, 1)) %>% 
  ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
             color = trt, shape = sprayer, label = emmean)) +
  geom_point(size = 3) +
  geom_jitter(data = auc_data %>% 
                rename(emmean = auc), alpha = 0.02) +
  scale_color_viridis_d(option = "H") +
  geom_text_repel(
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 545) +
  coord_flip() +
  scale_shape_manual(values = c(16, 1)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.2) +
  scale_y_continuous(breaks = c(0, 50, 100, 150, 200, 250)) +
  theme_few() +
  labs(x = NULL, y = "Area under the curve") +
  theme(legend.position = "none",
        legend.text = element_markdown(size = 20),
        legend.background = element_blank(),
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) -> figE
figE
```
```{r}
#https://easystats.github.io/blog/posts/bayestestr_emmeans/
auc_main <- pairs(emmeans(auc_model, ~ trt))

describe_posterior(auc_main,
                   centrality = "mean", dispersion = TRUE,
                   ci = .95, ci_method = "hdi",
                   test = c("bayesfactor"),
                   bf_prior = auc_model) %>% 
  tibble() -> auc_bf
readr::write_csv(path = "../supp_file/data/auc_bf.csv", x = auc_bf)
```

```{r}
#estimate_contrasts(auc_model, test = "bf") -> auc_bf
#auc_bf %>% 
#  tibble() -> auc_bf
#readr::write_csv(path = "../supp_file/data/auc_bf.csv", x = auc_bf)
```

```{r eval = FALSE}
#library(modelbased)
#estimate_contrasts(auc_model, test = "bf") %>% 
#  kableExtra::kable()
```
